Airspace configuration decision based on Monte-Carlo tree search

### 2018-04-13 article/article.tex
(+) Added algorithms
(+) Continued article

\usepackage{fontspec}
\usepackage{polyglossia}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{unicode-math}
\usepackage{amsmath,amsthm,stmaryrd}
\usepackage{algorithm,algpseudocode}

@@

In most cases the cost of a configuration is based on the workload. Each
approach seems to give their own representation of the workload. For instance,
~\cite{bedouet2016} determined workload density proportionally to the time
spent by aircraft in each sector. A simpler version~\cite{sergeeva2017dynamic}
only uses the number of aircraft. On the other hand, more complex methods,
involving many more inputs are also available. For instance
,~\cite{gianazza2010forecasting} used several indicators, such as sector
volume, or vertical incoming flows in the next 15 and 60 minutes. Those
indicators ease the training of a neural network forecasting the workload.

@@

@@

\section{Algorithm}
\subsection{Monte Carlo tree search overview}
\begin{algorithm}
  \caption{General MCTS~\cite{browne2012survey}}
  \begin{algorithmic}
    \Procedure{MctsSearch}{$v_0$}
    \While{within computational budget}
    \State{} \(v_l \gets\) \Call{TreePolicy}{$v_0$}
    \State{} \(\Delta \gets\) \Call{DefaultPolicy}{$s(v_l)$}
    \State{} \Call{Backup}{$v_l$, $\Delta$}
    \EndWhile{}
    \Return{\(a(\)\Call{BestChild}{$v_0$}\()\)}
    \EndProcedure{}
  \end{algorithmic}

\end{algorithm}

>>>>

\usepackage{fontspec}
\usepackage{polyglossia}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{unicode-math}
\usepackage{amsmath,amsthm,stmaryrd}
\usepackage{algorithm,algpseudocode}
\usepackage{paralist}

\DeclareMathOperator{\argmax}{argmax}

@@

In most cases the cost of a configuration is based on the workload. Each
approach seems to give their own representation of the workload. For instance,
~\cite{bedouet2016} determined workload density proportionally to the time
spent by aircraft in each sector. A simpler version~\cite{sergeeva2017dynamic}
only uses the number of aircraft. On the other hand, more complex methods,
involving many more inputs are also available. For
instance,~\cite{gianazza2010forecasting} used several indicators, such as sector
volume, or vertical incoming flows in the next 15 and 60 minutes. Those
indicators ease the training of a neural network forecasting the workload.

@@

\section{Algorithm}

The task of building an optimal sequence of partitions (lowering
as much as possible the workload of each controller) is fulfilled by a
stochastic tree search method, namely the Monte Carlo tree search. To assess the
exactness of the results, an exact method (here A\(^*\)) is used.

\subsection{Monte Carlo tree search overview}
Monte-Carlo is a best-first search method using stochastic simulations. It is
composed of four phases, namely
\begin{compactenum}
	\item selection,
	\item expansion,
	\item simulation,
	\item backpropagation.
\end{compactenum}
Those phases are repeated until a stopping criterium is reached,
see\ref{alg:gen_mcts} (memory usage or time).
\begin{algorithm}
	\caption{General MCTS~\cite{browne2012survey}}\label{alg:gen_mcts}
	\begin{algorithmic}
		\Procedure{MctsSearchTree}{$v_0$}
		\While{within computational budget}
		\State{} \([v^l_1, \dots, v^l_i] \gets\) \Call{TreePolicy}{$v_0$}
		\State{} \(\Delta \gets\) \Call{DefaultPolicy}{$v^l_i$}
		\State{} \(r \gets\) \Call{Reward}{$\Delta$}
		\State{} \Call{Backup}{$[v^l_1, \dots, v^l_i]$, $r$}
		\EndWhile{}
		\EndProcedure{}
	\end{algorithmic}
\end{algorithm}

\subsection{UCT selection}
\begin{algorithm}
	\caption{Extending the search tree}
	\begin{algorithmic}
		\Function{TreePolicy}{$v$}
		\State{} \([v_1, \dots, v_n] \gets\) \Call{Select}{$v$}
		\If{$v_n$ is terminal}
		\State{} \Return{$[v_1, \dots, v_n]$}
		\Else{}
		\State{} \([v_1, \dots, v_{n+1}] \gets\)
		\Call{Expand}{$[v_1, \dots, v_n]$}
		\State{} \Return{$[v_1, \dots, v_{n+1}]$}
		\EndIf{}
		\EndFunction{}
	\end{algorithmic}
	\begin{algorithmic}
		\Function{Select}{$v, a$}
		\If{$v$ is terminal or fully expanded}
		\State{} \Return{$[v, a]$}
		\Else{}
		\State{} fav\(\gets\) \Call{BestChild}{$v$}
		\State{} \Return{\Call{Select}{fav, $[v, a]$}}
		\EndIf{}
		\EndFunction{}
	\end{algorithmic}
	\begin{algorithmic}
		\Function{BestChild}{$v$}
		\State{} \Return{$\argmax\{\Call{UCB}{v'} |
		v' \text{\,children of\,} v\}$}
		\EndFunction{}
	\end{algorithmic}
\end{algorithm}

@@
